### 2017-03-02 README.Rmd
update README
include gh-pages version of dcos from pkgdown
- Also modifies Description with URL for EML
- and updates Readme not to say no CRAN version is available.

[![Travis-CI Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)

@@

`EML` has not yet been released.  You can install the current development version from rOpenSci using:

@@

Validate EML against the official schema

>>>>

[![Travis-CI Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)
[![codecov.io](https://codecov.io/github/ropensci/EML/coverage.svg?branch=master)](https://codecov.io/github/ropensci/EML?branch=master)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ropensci/EML?branch=master&svg=true)](https://ci.appveyor.com/project/ropensci/EML)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/EML)](http://cran.r-project.org/package=EML)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/EML)](http://cran.r-project.org/web/packages/EML/index.html)
[![Github Stars](https://img.shields.io/github/stars/ropensci/EML.svg?style=social&label=Github)](https://github.com/ropensci/EML)
[![DOI](https://zenodo.org/badge/10894022.svg)](https://zenodo.org/badge/latestdoi/10894022)

@@

You can install the current development version from rOpenSci using:

@@

Validation helps ensure that an EML file can be accurately interpreted by any computer program designed to read EML.  We can validate any EML against the official schema:
